Turbulence and Particle Acceleration in Giant Radio Haloes: the Origin of Seed Electrons

### 2016-06-23 paper.tex
more corrections: \dot{p}|_rad, alpha_inj, etc.

\author[A. Pinzke, S. Peng Oh and C. Pfrommer] 
{Anders Pinzke$^{1,2}$\thanks{apinzke@fysik.su.se (AP); peng@physics.ucsb.edu (SPO); christoph.pfrommer@h-its.org (CP)}, S. Peng Oh$^{3}$ and Christoph Pfrommer$^{4}$\footnotemark[1]\\
$^{1}$The Oskar Klein Centre for Cosmoparticle Physics, Stockholm University, AlbaNova University Center, SE - 106 91
  Stockholm, Sweden\\
$^{2}$Dark Cosmology Center, University of Copenhagen,
  Juliane Maries Vej 30, DK-2100 Copenhagen, Denmark\\
  $^{3}$University of California - Santa Barbara,
  Department of Physics, CA 93106-9530, USA\\
$^{4}$Heidelberg Institute for Theoretical Studies
  (HITS), Schloss-Wolfsbrunnenweg 35, 69118 Heidelberg, Germany}

@@

While analytic estimates have been made, there has been no ab initio
demonstration that structure formation can lead to the required
abundance of seed electrons with the correct spatial and spectral
characteristics. This is a non-trivial requirement: Coulomb cooling in
dense cluster cores is severe, and DSA fossil electrons may not
survive. On the other hand, for secondaries to constitute the seed
population, the CRp population required in the best-studied case of
the Coma cluster must have a very broad and flat (or even slightly
inverted) spatial profile \citep{brunetti12}, in contrast with the
thermal plasma whose energy density declines steeply with radius. In
Fig.~\ref{fig:Edens} we show that such a distribution is not predicted
by cosmological simulations \cite[see
  also][]{pinzke10,2014MNRAS.439.2662V}. If CRps are predominantly
advected with the cluster plasma, their distribution will be peaked
towards the cluster centre and shows a similar characteristics as the
thermal plasma. As a consequence, the distribution of secondary
electrons and the resulting radio synchrotron emission is also peaked
since the hadronic reaction is a two-body scattering process. Hence,
the simulated emission falls short of the observed extended and flat
radio profile of the Coma cluster.

@@

Given a seed population of CRs, we adopt essentially the same set of
plasma physics assumptions as the reacceleration model for RHs
\citep{brunetti07,brunetti11}. We solve the isotropic, gyro-phase
averaged Fokker-Planck equation (via a Crank-Nicholson scheme) for the
time evolution of the CRe distribution in the Lagrangian frame
\citep{brunetti07,brunetti11}:
\begin{eqnarray}
{{d f_{\rmn{e}}(p,t)}\over{d t}} &\!=&
\frac{\partial}{\partial p}
\left\{
f_{\rmn{e}}(p,t)\left[
\left|\frac{d p}{d t}\right|_{\rm Coul} 
+ \frac{p}{3}\left(\bnabla\bcdot \bvel\right)
+ \left|\frac{d p}{d t}\right|_{\rm rad}\right.\right.
\nonumber\\
&-& \left.\left.{1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right) 
\right]\right\} - \left(\bnabla\bcdot \bvel\right) f_{\rmn{e}}(p,t)
\nonumber\\
&+& {{\partial^2 }\over{\partial p^2}}
\left[
D_{pp} f_{\rmn{e}}(p,t) \right]+ Q_{\rmn{e}}\left[p,t;f_{\rmn{p}}(p,t)\right]   \, .
\label{elettroni}
\end{eqnarray}
Here $f_{\rmn{e}}$ is the one-dimensional distribution in position $x$
(suppressed for clarity), momentum $p$ and time $t$ (which is
normalised such that the number density is given by
$n_{\rmn{e}}(t)=\int d p f_{\rmn{e}}(p,t)$), $d/d t=\partial/\partial
t+\bvel\bcdot\bnabla$ is the Lagrangian derivative, $\bvel$ is the gas
velocity, $|d p/d t|$ represents Coulomb
\citep[Coul,][]{1972Phy....60..145G} and radiative
\citep[rad,][]{1979rpa..book.....R} losses, respectively,
\begin{eqnarray}
   \left|\frac{d p}{d t}\right|_{\rm Coul} &=& \frac{3\,\sigma_\rmn{T}\,n_{\rmn{e}}\,c}{2\, \beta_{\rmn{e}}^2}
  \left[\ln\left(\frac{m_{\rmn{e}} c^2 \beta_{\rmn{e}} \sqrt{\gamma-1}}{\hbar\,\omega_\rmn{plasma}}\right)\right.\nonumber \\
    &-&\ln(2)\left(\frac{\beta_{\rmn{e}}^2}{2}+\frac{1}{\gamma}\right)+\frac{1}{2}+
    \left.\left(\frac{\gamma-1}{4\gamma}\right)^2\right]\,, \\
  \left|\frac{d p}{d t}\right|_{\rm rad~} &=& \frac{4}{3}\frac{\sigma_\rmn{T}}{m_{\rmn{e}}c}\,
  \frac{p^2}{\beta_{\rmn{e}}}\,\left[1+\left(\frac{B}{B_\rmn{CMB}}\right)^2\right]\,.
\end{eqnarray}
Here $\beta_{\rmn{e}} = p/\sqrt{1+p^2}$ is the dimensionless velocity of CRs,
$\gamma=\sqrt{1+p^2}$ is the Lorentz factor of CRs,
$\omega_\rmn{plasma} = \sqrt{4\upi e^2 n_{\rmn{e}} / m_{\rmn{e}}}$ is the plasma
frequency, $n_e$ is the number density of free electrons, and
$\sigma_\rmn{T}= 8\upi e^4/3(m_{\rmn{e}} c^2)^2$ is the Thomson cross
section. The {\it rms} magnetic field strength is denoted by $B$ and
the equivalent field strength of the cosmic-microwave background is
given by $B_\rmn{CMB} = 3.24 (1 + z)^2\umu\rmn{G}$, where $z$ denotes
the redshift. In the peripheral cluster regions, where $B \ll
B_\rmn{CMB}$, the CRes loose virtually all their energy by means of
inverse Compton emission. $D_{pp}$ is the momentum space diffusion
coefficient (see \S\ref{sec:reacc}), and
$Q_{\rmn{e}}$ denotes the injection rate of primary and secondary
electrons in the ICM (see Sect.~\ref{sec:cosmo_sim}). The first term
containing the expression $\bnabla\bcdot \bvel$ represents Fermi-I
acceleration and the second term of this form describes adiabatic
gains and losses.

@@

The time evolution of the spectral energy distribution of CRps,
$f_{\rmn{p}}$, is similarly given by:
\begin{eqnarray}
\lefteqn{
  {{d f_{\rmn{p}}(p,t)}\over{d t}} =
  {{\partial }\over{\partial p}}
  \left\{
  f_{\rmn{p}}(p,t)\left[ \left|{{d p}\over{d t}}\right|_{\rm Coul}
    + \frac{p}{3}\bnabla\bcdot \left(\bvel+\bvel_{\rmn{st}}\right)\right.\right.}
\nonumber\\
&&-\left.\left. {1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right)
\right]\right\} - f_{\rmn{p}}(p,t) \bnabla\bcdot \left(\bvel+\bvel_{\rmn{st}}\right) 
- \bvel_{\rmn{st}}\bcdot\bnabla f_{\rmn{p}}(p,t)
\nonumber\\
&&+\,\,\, {{\partial^2 }\over{\partial p^2}}
\left[ D_{pp} f_{\rmn{p}}(p,t) \right] - {{f_{\rmn{p}}(p,t)}\over{\tau_{\rm had}(p)}}
+ Q_{\rmn{p}}(p,t)\, ,
\label{eq:FP_p}
\end{eqnarray}
where $\bvel_{\rmn{st}}=-\varv_{\rmn{A}}\bnabla f_{\rmn{p}}/|\bnabla
f_{\rmn{p}}|$ is the streaming velocity in the isotropic transport
approximation, $\varv_{\rmn{A}}$ is the Alfv\'en speed,
and $Q_{\rmn{p}}(p,t)$ denotes the injection rate of shock accelerated
CRps as a function of momentum $p$ and time $t$ (see
Sect.~\ref{sec:cosmo_sim}). The timescale of
hadronic losses that produce pions via CRp collisions with thermal
protons of the ICM is given by 
\begin{eqnarray}
  \tau_{\rm had} = \left[c\,n_\rmn{th}\,\sigma^{+/-,0}(p)\right]^{-1}\,,
\end{eqnarray}
where we use the cross-section, $\sigma^{+/-,0}(p)$, given by the
fitting formula in \citet{1986ApJ...307...47D}.

@@

All of the physics of turbulent reacceleration is effectively encapsulated in the diffusion coefficient \citep{brunetti07}, which can be rewritten as \citep{miniati15}:
\begin{equation}
D_{pp}(p) = \frac{ p^{2} \upi I_{\theta}(c_{s}/c)}{8 c} \langle k \rangle_{\mathcal{W}} \langle (\delta \varv_{\rm c})^{2} \rangle
\label{eqn:diffusion}
\end{equation}
where $I_{\theta}$ averages interaction rates over the CR pitch angle $\theta$; $I_{\theta} \approx 5$ for ICM conditions, and
\begin{equation}
\langle k \rangle_{\mathcal{W}} = \frac{1}{\langle (\delta \varv_{\rm c})^{2} \rangle} \int_{k_L}^{k_{\rm cut}} d k \, k \, \mathcal{W}(k) \approx \frac{s-1}{2-s} k_L \left( \frac{k_{\rm cut}}{k_L} \right)^{2-s} 
\label{eqn:k_W} 
\end{equation}
is an energy-averaged wavenumber, $k_L, k_{\rm cut}$ are the wavenumbers associated with the outer scale $L$ and the cutoff scale respectively, and we have assumed a total energy spectrum (composed of both kinetic and potential energy, where the two are assumed to be in equipartition, \citealt{sarkar11}): 
\begin{equation}
\mathcal{W}(k) = \frac{(s-1) \langle (\delta \varv_{\rm c})^{2} \rangle}{k_L} \left( \frac{k}{k_L} \right)^{-s} 
\label{eqn:Wk}
\end{equation}
which defines the normalisation $\langle (\delta \varv_{\rm c})^{2} \rangle$ (the subscript 'c' emphasizes that we specialise to compressive modes). Intuitively, we can understand the form of the the diffusion coefficient from the fact that for second-order Fermi acceleration, $\dot{p} \sim \Delta p/\tau \sim p\,\langle k c \rangle_{\mathcal{W}} (\delta \varv_{\rm c}/c)^{2}$, where $\tau^{-1} \sim \langle k c \rangle_{\mathcal{W}}$ is the energy averaged wave-particle interaction rate, and $\Delta p \sim p (\delta \varv_{\rm c}/c)^{2}$ is the typical momentum change during wave particle scattering. Thus: 
\begin{equation}
D_{pp} \sim p \dot{p} \sim p^{2} \langle k c \rangle_{\mathcal{W}} \left( \frac{\delta \varv_{\rm c}}{c} \right)^{2}. 
\end{equation}

@@

Since the standard vanilla model requires a CR seed population which is
inconsistent with the simulations (Fig \ref{fig:Edens}), some modifications are
necessary, either in the seed CR population or in the properties of
turbulence. We focus on three scenarios. (i) In model {\em M-primaries}, we
assume that CR electrons, which have been accelerated by cosmic formation shocks
and successively cooled by inverse Compton and synchrotron losses, form a fossil
seed population for reacceleration. (ii) In model {\em M-streaming}, we account
for the outward streaming of central CRps, which produces a flat CR distribution
in the ICM and equivalently a flat secondary seed population of CRes for
reacceleration. (iii) In model {\em M-turbulence} we adopt a spatially flatter
turbulent profile than what was adopted before but assume that seed CRps and
secondary CRes follow the steep profile that is suggested by structure formation
simulations.

@@

We limit the acceleration efficiency to $\zeta_\rmn{max}$ by
steepening the spectral index of the injected population
$\alpha_\rmn{inj}$ to $\alpha_\rmn{sub}$ so that $\zeta_\rmn{lin}
\leq \zeta_\rmn{max}$ is always fulfilled. The slope
$\alpha_\rmn{inj}$ impact $\zeta_\rmn{inj}$ via the mean energy per
particle, $\eps_\rmn{p}/n_\rmn{p}$. This
procedure conserves energy and is motivated by models of non-linear
shock acceleration where a sub-shock with a lower compression ratio
(and hence steeper spectral index) forms
\citep[e.g.,][]{2000ApJ...540..292E}. Given our assumed $\eb=0.23$, we
find that for strong shocks where $\alpha \lesssim 2.3$ the spectral
slope is steepened by a maximum of $\sim 10$ per cent in low
temperature regimes ($\kB T\sim 0.1$~keV), while the steepening is much
smaller for high temperature regimes ($\kB T\sim 10$~keV) that are more
relevant for clusters. Since $p_\rmn{inj}$ remains fixed, so does the
CR number density $n_\CR$. Hence we can solve for the
renormalised normalisation constant $C_\rmn{sub}$ using $n_\CR$
and Eqn.~\ref{eq:eta}:
\begin{equation}
  \label{eq:Cp_sub}
  C_\rmn{sub}=\eta_\rmn{p,lin}\,(\alpha_\rmn{sub}-1)\,p_\rmn{inj}^{\alpha_\rmn{sub}-1}\,,
\end{equation}
where the new distribution function is given by $f_\p(p,t)= C_\rmn{sub}
p^{-\alpha_\rmn{sub}}$. We set an upper limit on the ratio of
accelerated proton-to-dissipated energy in the downstream of strong
shocks that varies from $\zeta_\rmn{max} \sim 0.01-0.1$, depending on
the adopted model (for more details, see Section \ref{sec:results}).

@@

In Fig.~\ref{fig:sync_profile}, we show radial profiles for the radio
emission in all three scenarios in which the seeds undergo Fermi-II
reacceleration in turbulent fields that are shaped such as to
reproduce the Coma RH profile at 352~MHz.  Adopting our
parametrization for the volumetric injection rate of turbulent energy,
$I_0\propto \eps_\rmn{th}^{\alpha_\rmn{tu}}$, we find that to fit the observations, we require
$\alpha_\rmn{tu}= 0.67$ for \Mflatturb, $\alpha_\rmn{tu}= 0.82$ for
\Mstream, and $\alpha_\rmn{tu}= 0.88$ for \Mprimary. As a result, the
ratio of turbulent-to-thermal energy densities slightly increase with
radius as shown in Fig.~\ref{fig:turb}.  The fine-tuning of these exponents is somewhat problematic, as we discuss in \S\ref{sect:param_comp}. After turbulent
reacceleration, the volume-weighted, relative CRp energy density and
relative CRp number density inside the RH for \Mflatturb (\Mstream),
are found to be 2 (3) per cent and $2\times10^{-8}$ ($5\times10^{-8}$),
respectively.

@@

Figure~\ref{fig:sync_profile} demonstrates that the modelled radio
profiles without turbulent reacceleration are too steep.  In the
bottom right panel of Fig.~\ref{fig:sync_profile} (labelled with
Brunetti et al. 2012), we show that our simulated profiles of
reaccelerated CRs, which only take advective CR transport into
account, i.e. they neglect CR streaming or a flatter turbulent
profile, produce radio profiles that are too steep. Indeed, even using
the assumptions of previous work -- where complete freedom in the seed
population was allowed -- it is not possible to reproduce observations
in both frequencies in any model.\footnote{Note that in previous work
  on the Coma cluster, $\eps_\rmn{turb} \propto \eps_\rmn{th}$ was
  adopted which approximately corresponds to $\alpha_\rmn{tu}= 1$
  \citep{brunetti12} and together with the different distributions for
  seed CRes constitute the main differences compared to our work.}
Decreasing the acceleration efficiency with radius does not change
this conclusion much because of the weak radial dependence of
$D_{pp}(R)\propto \eps_\rmn{th}(R)^{\alpha_\rmn{tu}-1}
\sqrt{T(R)}$. This signals that the problem is generic and requires
either additional modifications to the plasma physics of acceleration
or a better understanding of potential observational systematics. In
addition there are differences in the simulated density and
temperature profiles in comparison to the observed profile in Coma
that impact the CR abundance as well as cooling and reacceleration.

In Fig.~\ref{fig:tauD} we show how the turbulent reacceleration
timescales in our three models scale with radius. As expected, the
\Mprimary model with $\alpha_\rmn{tu}=0.88$ has the flattest profile
with $\tau_{\rm D}\approx0.4\,\rmn{Gyr}$, where the small dip at large
radius driven by the decrease in thermal energy density. The
\Mflatturb model has the the flattest turbulent profile parametrized
by the smaller $\alpha_\rmn{tu}$ which explains the steepest $\tau_{\rm D}$
profile. Note that a fixed reacceleration timescale is required to
explain the observations at each radius and for each model (see also
Table~\ref{tab:timescales}). Since $\tau_\rmn{cl} \propto X_\rmn{tu}^2 k_L$,
these two parameters are degenerate and can be traded off one another.

@@

In order to quickly explore this parameter space, we solve the
Fokker-Planck equation in static spherical shells for injection,
reacceleration, and losses of the CRs, i.e., we neglect Lagrangian
evolution during re-acceleration.  This ignores the effect of
adiabatic compressive heating of the CRs, though this is generally
subdominant (e.g., see Fig. 7 of \citealt{miniati15}). Once
the CRs have been reaccelerated for $\tau_\rmn{cl} = 650\,\rmn{Myr}$,
we calculate the resulting radio emission numerically using the
formalism outlined in \cite{1979rpa..book.....R} and compare the
emission profiles and spectra as we vary one parameter at a time
relative to our fiducial model.

@@

{\bf Impact of overall level of turbulence ($X_{\rm tu}$).} From the top panels of Fig.~\ref{fig:param_comp}, we see that as $X_{\rm tu}$ increases, there are 3 important changes: an exponential increase in radio luminosity, a flattening of the radio surface brightness profile, and an increase in spectral curvature. We discuss these in turn.

>>>>

\author[A. Pinzke, S. Peng Oh and C. Pfrommer] 
{Anders Pinzke$^{1,2}$\thanks{apinzke@fysik.su.se (AP); peng@physics.ucsb.edu (SPO); christoph.pfrommer@h-its.org (CP)}, S. Peng Oh$^{3}$\footnotemark[1], and Christoph Pfrommer$^{4}$\footnotemark[1]\\
$^{1}$The Oskar Klein Centre for Cosmoparticle Physics, Stockholm University, AlbaNova University Center, SE - 106 91
  Stockholm, Sweden\\
$^{2}$Dark Cosmology Center, University of Copenhagen,
  Juliane Maries Vej 30, DK-2100 Copenhagen, Denmark\\
  $^{3}$University of California - Santa Barbara,
  Department of Physics, CA 93106-9530, USA\\
$^{4}$Heidelberg Institute for Theoretical Studies
  (HITS), Schloss-Wolfsbrunnenweg 35, 69118 Heidelberg, Germany}

@@

While analytic estimates have been made, there has been no ab initio
demonstration that structure formation can lead to the required
abundance of seed electrons with the correct spatial and spectral
characteristics. This is a non-trivial requirement: Coulomb cooling in
dense cluster cores is severe, and DSA fossil electrons may not
survive. On the other hand, for secondaries to constitute the seed
population, the CRp population required in the best-studied case of
the Coma cluster must have a very broad and flat (or even slightly
inverted) spatial profile \citep{brunetti12}, in contrast with the
thermal plasma whose energy density declines steeply with radius. In
Figure~\ref{fig:Edens} we show that such a distribution is not predicted
by cosmological simulations \cite[see
  also][]{pinzke10,2014MNRAS.439.2662V}. If CRps are predominantly
advected with the cluster plasma, their distribution will be peaked
towards the cluster centre and shows a similar characteristics as the
thermal plasma. As a consequence, the distribution of secondary
electrons and the resulting radio synchrotron emission is also peaked
since the hadronic reaction is a two-body scattering process. Hence,
the simulated emission falls short of the observed extended and flat
radio profile of the Coma cluster.

@@

Given a seed population of CRs, we adopt essentially the same set of
plasma physics assumptions as the reacceleration model for RHs
\citep{brunetti07,brunetti11}. We solve the isotropic, gyro-phase
averaged Fokker-Planck equation (via a Crank-Nicholson scheme) for the
time evolution of the CRe distribution in the Lagrangian frame
\citep{brunetti07,brunetti11}:
\begin{eqnarray}
{{d f_{\rmn{e}}(p,t)}\over{d t}} &\!=&
\frac{\partial}{\partial p}
\left\{
f_{\rmn{e}}(p,t)\left[
\left|\frac{d p}{d t}\right|_{\rm Coul} 
+ \frac{p}{3}\left(\bnabla\bcdot \bvel\right)
+ \left|\frac{d p}{d t}\right|_{\rm rad}\right.\right.
\nonumber\\
&-& \left.\left.{1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right) 
\right]\right\} - \left(\bnabla\bcdot \bvel\right) f_{\rmn{e}}(p,t)
\nonumber\\
&+& {{\partial^2 }\over{\partial p^2}}
\left[
D_{pp} f_{\rmn{e}}(p,t) \right]+ Q_{\rmn{e}}\left[p,t;f_{\rmn{p}}(p,t)\right]   \, .
\label{elettroni}
\end{eqnarray}
Here $f_{\rmn{e}}$ is the one-dimensional distribution in position $x$
(suppressed for clarity), momentum $p=P/(m_{\rmn{e}} c)$ and time $t$ (which is
normalised such that the number density is given by
$n_{\rmn{CRe}}(t)=\int d p f_{\rmn{e}}(p,t)$), $d/d t=\partial/\partial
t+\bvel\bcdot\bnabla$ is the Lagrangian derivative, $\bvel$ is the gas
velocity, $|d p/d t|$ represents Coulomb
\citep[Coul,][]{1972Phy....60..145G} and radiative
\citep[rad,][]{1979rpa..book.....R} losses, respectively,
\begin{eqnarray}
   \left|\frac{d p}{d t}\right|_{\rm Coul} &=& \frac{3\,\sigma_\rmn{T}\,n_{\rmn{e}}\,c}{2\, \beta_{\rmn{e}}^2}
  \left[\ln\left(\frac{m_{\rmn{e}} c^2 \beta_{\rmn{e}} \sqrt{\gamma-1}}{\hbar\,\omega_\rmn{plasma}}\right)\right.\nonumber \\
    &-&\ln(2)\left(\frac{\beta_{\rmn{e}}^2}{2}+\frac{1}{\gamma}\right)+\frac{1}{2}+
    \left.\left(\frac{\gamma-1}{4\gamma}\right)^2\right]\,, \\
  \left|\frac{d p}{d t}\right|_{\rm rad~} &=& \frac{4}{3}\frac{\sigma_\rmn{T}}{m_{\rmn{e}}c}\,
  \frac{p^2}{\beta_{\rmn{e}}}\,\left[1+\left(\frac{B}{B_\rmn{CMB}}\right)^2\right]\,\eps_{\rmn{CMB}}\,.
\end{eqnarray}
Here $\beta_{\rmn{e}} = p/\sqrt{1+p^2}$ is the dimensionless velocity of CRs,
$\gamma=\sqrt{1+p^2}$ is the Lorentz factor of CRs,
$\omega_\rmn{plasma} = \sqrt{4\upi e^2 n_{\rmn{e}} / m_{\rmn{e}}}$ is the plasma
frequency, $n_e$ is the number density of free electrons, and
$\sigma_\rmn{T}= 8\upi e^4/3(m_{\rmn{e}} c^2)^2$ is the Thomson cross
section. The {\it rms} magnetic field strength is denoted by $B$ and
the equivalent field strength of the cosmic-microwave background is
given by $B_\rmn{CMB} = 3.24 (1 + z)^2\umu\rmn{G}$, where $z$ denotes
the redshift. In the peripheral cluster regions, where $B \ll
B_\rmn{CMB}$, the CRes loose virtually all their energy by means of
inverse Compton emission. $D_{pp}$ is the momentum space diffusion
coefficient (see \S\ref{sec:reacc}), and
$Q_{\rmn{e}}$ denotes the injection rate of primary and secondary
electrons in the ICM (see section~\ref{sec:cosmo_sim}). The first term
containing the expression $\bnabla\bcdot \bvel$ represents Fermi-I
acceleration and the second term of this form describes adiabatic
gains and losses.

@@

The time evolution of the spectral energy distribution of CRps,
$f_{\rmn{p}}$, is similarly given by:
\begin{eqnarray}
\lefteqn{
  {{d f_{\rmn{p}}(p,t)}\over{d t}} =
  {{\partial }\over{\partial p}}
  \left\{
  f_{\rmn{p}}(p,t)\left[ \left|{{d p}\over{d t}}\right|_{\rm Coul}
    + \frac{p}{3}\bnabla\bcdot \left(\bvel+\bvel_{\rmn{st}}\right)\right.\right.}
\nonumber\\
&&-\left.\left. {1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right)
\right]\right\} - f_{\rmn{p}}(p,t) \bnabla\bcdot \left(\bvel+\bvel_{\rmn{st}}\right) 
- \bvel_{\rmn{st}}\bcdot\bnabla f_{\rmn{p}}(p,t)
\nonumber\\
&&+\,\,\, {{\partial^2 }\over{\partial p^2}}
\left[ D_{pp} f_{\rmn{p}}(p,t) \right] - {{f_{\rmn{p}}(p,t)}\over{\tau_{\rm had}(p)}}
+ Q_{\rmn{p}}(p,t)\, ,
\label{eq:FP_p}
\end{eqnarray}
where $\bvel_{\rmn{st}}=-\varv_{\rmn{A}}\bnabla f_{\rmn{p}}/|\bnabla
f_{\rmn{p}}|$ is the streaming velocity in the isotropic transport
approximation, $\varv_{\rmn{A}}$ is the Alfv\'en speed,
and $Q_{\rmn{p}}(p,t)$ denotes the injection rate of shock accelerated
CRps as a function of momentum $p=P/(m_{\rmn{p}} c)$ and time $t$ (see
section~\ref{sec:cosmo_sim}). The timescale of
hadronic losses that produce pions via CRp collisions with thermal
protons of the ICM is given by 
\begin{eqnarray}
  \tau_{\rm had} = \left[c\,n_\rmn{th}\,\sigma^{+/-,0}(p)\right]^{-1}\,,
\end{eqnarray}
where we use the cross-section, $\sigma^{+/-,0}(p)$, given by the
fitting formula in \citet{1986ApJ...307...47D}.

@@

All of the physics of turbulent reacceleration is effectively encapsulated in the diffusion coefficient \citep{brunetti07}, which can be rewritten as \citep{miniati15}:
\begin{equation}
D_{pp}(p) = \frac{ p^{2} \upi I_{\theta}(c_{s}/c)}{8 c} \langle k \rangle_{\mathcal{W}} \langle (\delta \varv_{\rm c})^{2} \rangle
\label{eqn:diffusion}
\end{equation}
where $I_{\theta}$ averages interaction rates over the CR pitch angle $\theta$; $I_{\theta} \approx 5$ for ICM conditions, and
\begin{equation}
\langle k \rangle_{\mathcal{W}} = \frac{1}{\langle (\delta \varv_{\rm c})^{2} \rangle} \int_{k_L}^{k_{\rm cut}} d k \, k \, \mathcal{W}(k) \approx \frac{s-1}{2-s} k_L \left( \frac{k_{\rm cut}}{k_L} \right)^{2-s} 
\label{eqn:k_W} 
\end{equation}
is an energy-averaged wavenumber, $k_L, k_{\rm cut}$ are the wavenumbers associated with the outer scale $L$ and the cutoff scale respectively, and we have assumed a total energy spectrum (composed of both kinetic and potential energy, where the two are assumed to be in equipartition, \citealt{sarkar11}): 
\begin{equation}
\mathcal{W}(k) = \frac{(s-1) \langle (\delta \varv_{\rm c})^{2} \rangle}{k_L} \left( \frac{k}{k_L} \right)^{-s} 
\label{eqn:Wk}
\end{equation}
which defines the normalisation $\langle (\delta \varv_{\rm c})^{2} \rangle$ (the subscript 'c' emphasizes that we specialise to compressive modes). Intuitively, we can understand the form of the the diffusion coefficient from the fact that for second-order Fermi acceleration, $\dot{p} \sim \Delta p/\tau \sim p\,\langle k c \rangle_{\mathcal{W}} (\delta \varv_{\rm c}/c)^{2}$, where $\tau^{-1} \sim \langle k c \rangle_{\mathcal{W}}$ is the energy averaged wave-particle interaction rate, and $\Delta p \sim p (\delta \varv_{\rm c}/c)^{2}$ is the typical momentum change during wave-particle scattering. Thus: 
\begin{equation}
D_{pp} \sim p \dot{p} \sim p^{2} \langle k c \rangle_{\mathcal{W}} \left( \frac{\delta \varv_{\rm c}}{c} \right)^{2}. 
\end{equation}

@@

Since the standard vanilla model requires a CR seed population which is
inconsistent with the simulations (Figure~\ref{fig:Edens}), some modifications are
necessary, either in the seed CR population or in the properties of
turbulence. We focus on three scenarios. (i) In model {\em M-primaries}, we
assume that CR electrons, which have been accelerated by cosmic formation shocks
and successively cooled by inverse Compton and synchrotron losses, form a fossil
seed population for reacceleration. (ii) In model {\em M-streaming}, we account
for the outward streaming of central CRps, which produces a flat CR distribution
in the ICM and equivalently a flat secondary seed population of CRes for
reacceleration. (iii) In model {\em M-turbulence} we adopt a spatially flatter
turbulent profile than what was adopted before but assume that seed CRps and
secondary CRes follow the steep profile that is suggested by structure formation
simulations.

@@

We limit the acceleration efficiency to $\zeta_\rmn{max}$ by
steepening the spectral index of the injected population
$\alpha_\rmn{inj}$ to $\alpha_\rmn{sub}$ so that $\zeta_\rmn{lin}
\leq \zeta_\rmn{max}$ is always fulfilled. The slope
$\alpha_\rmn{inj}$ impact $\zeta_\rmn{inj}$ via the mean energy per
particle, $\eps_\rmn{p}/n_\rmn{p}$. This
procedure conserves energy and is motivated by models of non-linear
shock acceleration where a sub-shock with a lower compression ratio
(and hence steeper spectral index) forms
\citep[e.g.,][]{2000ApJ...540..292E}. Given our assumed $\eb=0.23$, we
find that for strong shocks where $\alpha_{\rmn{inj}} \lesssim 2.3$ the spectral
slope is steepened by a maximum of $\sim 10$ per cent in low
temperature regimes ($\kB T\sim 0.1$~keV), while the steepening is much
smaller for high temperature regimes ($\kB T\sim 10$~keV) that are more
relevant for clusters. Since $p_\rmn{inj}$ remains fixed, so does the
CR number density $n_\CR$. Hence we can solve for the
renormalised normalisation constant $C_\rmn{sub}$ using $n_\CR$
and Eqn.~\ref{eq:eta}:
\begin{equation}
  \label{eq:Cp_sub}
  C_\rmn{sub}=\eta_\rmn{p,lin}\,(\alpha_\rmn{sub}-1)\,p_\rmn{inj}^{\alpha_\rmn{sub}-1}\,,
\end{equation}
where the new distribution function is given by $f_\p(p,t)= C_\rmn{sub}
p^{-\alpha_\rmn{sub}}$. We set an upper limit on the ratio of
accelerated proton-to-dissipated energy in the downstream of strong
shocks that varies from $\zeta_\rmn{max} \sim 0.01-0.1$, depending on
the adopted model (for more details, see section~\ref{sec:results}).

@@

In Figure~\ref{fig:sync_profile}, we show radial profiles for the radio
emission in all three scenarios in which the seeds undergo Fermi-II
reacceleration in turbulent fields that are shaped such as to
reproduce the Coma RH profile at 352~MHz.  Adopting our
parametrization for the volumetric injection rate of turbulent energy,
$I_0\propto \eps_\rmn{th}^{\alpha_\rmn{tu}}$, we find that to fit the observations, we require
$\alpha_\rmn{tu}= 0.67$ for \Mflatturb, $\alpha_\rmn{tu}= 0.82$ for
\Mstream, and $\alpha_\rmn{tu}= 0.88$ for \Mprimary. As a result, the
ratio of turbulent-to-thermal energy densities slightly increase with
radius as shown in Figure~\ref{fig:turb}.  The fine-tuning of these exponents is somewhat problematic, as we discuss in \S\ref{sect:param_comp}. After turbulent
reacceleration, the volume-weighted, relative CRp energy density and
relative CRp number density inside the RH for \Mflatturb (\Mstream),
are found to be 2 (3) per cent and $2\times10^{-8}$ ($5\times10^{-8}$),
respectively.

@@

Figure~\ref{fig:sync_profile} demonstrates that the modelled radio
profiles without turbulent reacceleration are too steep.  In the
bottom right panel of Figure~\ref{fig:sync_profile} (labelled with
Brunetti et al. 2012), we show that our simulated profiles of
reaccelerated CRs, which only take advective CR transport into
account, i.e. they neglect CR streaming or a flatter turbulent
profile, produce radio profiles that are too steep. Indeed, even using
the assumptions of previous work -- where complete freedom in the seed
population was allowed -- it is not possible to reproduce observations
in both frequencies in any model.\footnote{Note that in previous work
  on the Coma cluster, $\eps_\rmn{turb} \propto \eps_\rmn{th}$ was
  adopted which approximately corresponds to $\alpha_\rmn{tu}= 1$
  \citep{brunetti12} and together with the different distributions for
  seed CRes constitute the main differences compared to our work.}
Decreasing the acceleration efficiency with radius does not change
this conclusion much because of the weak radial dependence of
$D_{pp}(R)\propto \eps_\rmn{th}(R)^{\alpha_\rmn{tu}-1}
\sqrt{T(R)}$. This signals that the problem is generic and requires
either additional modifications to the plasma physics of acceleration
or a better understanding of potential observational systematics. In
addition there are differences in the simulated density and
temperature profiles in comparison to the observed profile in Coma
that impact the CR abundance as well as cooling and reacceleration.

In Figure~\ref{fig:tauD} we show how the turbulent reacceleration
timescales in our three models scale with radius. As expected, the
\Mprimary model with $\alpha_\rmn{tu}=0.88$ has the flattest profile
with $\tau_{\rm D}\approx0.4\,\rmn{Gyr}$, where the small dip at large
radius driven by the decrease in thermal energy density. The
\Mflatturb model has the the flattest turbulent profile parametrized
by the smaller $\alpha_\rmn{tu}$ which explains the steepest $\tau_{\rm D}$
profile. Note that a fixed reacceleration timescale is required to
explain the observations at each radius and for each model (see also
Table~\ref{tab:timescales}). Since $\tau_\rmn{cl} \propto X_\rmn{tu}^2 k_L$,
these two parameters are degenerate and can be traded off one another.

@@

In order to quickly explore this parameter space, we solve the
Fokker-Planck equation in static spherical shells for injection,
reacceleration, and losses of the CRs, i.e., we neglect Lagrangian
evolution during re-acceleration.  This ignores the effect of
adiabatic compressive heating of the CRs, though this is generally
subdominant (e.g., see Figure~7 of \citealt{miniati15}). Once
the CRs have been reaccelerated for $\tau_\rmn{cl} = 650\,\rmn{Myr}$,
we calculate the resulting radio emission numerically using the
formalism outlined in \cite{1979rpa..book.....R} and compare the
emission profiles and spectra as we vary one parameter at a time
relative to our fiducial model.

@@

{\bf Impact of overall level of turbulence ($X_{\rm tu}$).} From the top panels of Figure~\ref{fig:param_comp}, we see that as $X_{\rm tu}$ increases, there are 3 important changes: an exponential increase in radio luminosity, a flattening of the radio surface brightness profile, and an increase in spectral curvature. We discuss these in turn.
